Unshuffling Permutations

### 2015-09-12 article.tex
reduction

  \begin{proof}[of Claim~\ref{claim: all (nu_2, nu'_2)-edges}]
    Suppose, aiming at a contradiction, that
    $\mathcal{M}$ does not contain $N_2$ $(\nu_2, \nu'_2)$-edge.
    Combing Claim~\ref{claim:no (nu_1, nu_2)-edge} and
    Claim~\ref{claim:one (nu_2, nu'_2)-edge},
    we conclude that there exists a position $a$ in $\nu_2$ that is
    involded in an edge $(a, a')$ in $\mathcal{M}$ that is
    neither a $\nu_1, \nu_2)$-edge,
    nor a $(\nu_2, \nu_2)$-edge.
    Furthermore, according to Claim~\ref{claim:one (nu_2, nu'_2)-edge},
    there exists a $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
    Then, we have
    $\mu(x) < \mu(a)$ (since $\nu_1$ is below $\nu'_1$) and
    $\mu(x') < \mu(a')$ (since $\nu'_1$ is above any other gadget),
    which contradicts our hypothesis.
    \qed
  \end{proof}

>>>>

  \begin{proof}[of Claim~\ref{claim: all (nu_2, nu'_2)-edges}]
    Suppose, aiming at a contradiction, that
    $\mathcal{M}$ does not contain $N_2$ $(\nu_2, \nu'_2)$-edge.
    According to Claim~\ref{claim:one (nu_2, nu'_2)-edge},
    there exists a $(\nu_2; \nu'_2)$-edge $(a, a')$ in $\mathcal{M}$.
    Combing Claim~\ref{claim:no (nu_1, nu_2)-edge},
    Claim~\ref{claim:no (nu_2, nu'_1)-edge}  and
    Claim~\ref{claim:one (nu_2, nu'_2)-edge},
    we conclude that there exists a position $x$ in $\nu_2$ that is
    involded in an edge $(x, x')$ in $\mathcal{M}$ that is
    neither a $\nu_1, \nu_2)$-edge,
    nor a $(\nu_2, \nu_2)$-edge,
    nor a $(\nu_2, \nu'_1)$-edge
    nor a $(\nu_2, \nu'_2)$-edge (our hypothesis).
    We need to consider two cases.
    \begin{itemize}
      \item
      $(x, x')$ is
      either a $(\nu_2, \nu'_3)$-edge
      or a $(\nu_2, \pi')$-edge
      or a $(\nu_2, \nu'_4)$-edge
      or a $(\nu_2, \pi'')$-edge
      or a $(\nu_2, \sigma'')$-edge.
      Since $\mathcal{M}$ is containment-free,
      we must have $a < x$.
      Then it follows that
      $\mu(a) > \mu(x)$ (since $\nu_2$ is decreasing) and
      $\mu(a') < \mu(x')$
      (since $\nu'_3$, $\pi'$, $\nu'_4$, $\pi''$ and $\sigma''$ are all above
      $\nu'_2$),
      which contradicts our hypothesis.
      \item
      $(x, x')$ is
      either a $(\nu_2, \nu_3)$-edge
      or a $(\nu_2, \sigma')$-edge
      or a $(\nu_2, \nu_4)$-edge.
    \end{itemize}
    Furthermore, according to Claim~\ref{claim:one (nu_2, nu'_2)-edge},
    there exists a $(\nu_1, \nu'_1)$-edge in $\mathcal{M}$.
    Then, we have
    $\mu(x) < \mu(a)$ (since $\nu_1$ is below $\nu'_1$) and
    $\mu(x') < \mu(a')$ (since $\nu'_1$ is above any other gadget),
    which contradicts our hypothesis.
    \qed
  \end{proof}
